\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\begin{document}

% Setting up the title
\title{Frequently Asked Questions (FAQs) for SecureGen AI}
\author{}
\date{\today}
\maketitle

% Question 1: Overview of the solution
\section*{What is SecureGen AI?}
SecureGen AI is a network intrusion detection system that combines signature-based detection using Suricata with anomaly-based detection powered by machine learning. It leverages federated learning for collaborative, privacy-preserving model training.

% Question 2: How the system operates
\section*{How does SecureGen AI work?}
The Service captures network packets and uses Suricata for signature-based detection of known threats. Benign packets are analyzed using machine learning models trained via federated learning to detect anomalies. Detected anomalies generate new rules for future detection, enhancing adaptability.

% Question 3: Benefits of the solution
\section*{What are the benefits of using SecureGen AI?}
\begin{itemize}
    \item \textbf{Enhanced Accuracy:} Combines signature and anomaly-based detection for improved threat detection.
    \item \textbf{Privacy Preservation:} Uses federated learning and encryption to keep data local.
    \item \textbf{Adaptability:} Continuously updates rules to address new threats.
\end{itemize}

% Question 4: Data protection measures
\section*{How is my data protected?}
Your raw network data remains local. Only encrypted model parameters are shared for federated learning, secured with CKKS homomorphic encryption and verified using Halo2 zero-knowledge proofs.

% Question 5: Organizational use
\section*{Can I use SecureGen AI for my organization?}
Yes, SecureGen AI is designed for organizations seeking advanced network security with privacy compliance. Contact our sales team at huzaifamateen426@gmail.com for deployment options.

% Question 6: Training datasets
\section*{What datasets are used for training the model?}
The model is trained on standardized datasets, including UNSW-NB15, Bot-IoT, ToN-IoT, and CSE-CIC-IDS2018, converted to NetFlow-based feature sets.

% Question 7: Model update frequency
\section*{How often is the model updated?}
The model is updated periodically through federated learning rounds, incorporating new data from participating organizations to enhance detection capabilities.

% Question 8: Regulatory compliance
\section*{Is SecureGen AI compliant with data protection regulations?}
Yes, the Service is designed to comply with regulations like GDPR by ensuring raw data stays local and using privacy-preserving techniques.

% Question 9: Getting started
\section*{How do I get started with SecureGen AI?}
Contact our sales team at huzaifamateen426@gmail.com to discuss deployment options, including cloud-based or on-premise solutions, and subscription plans.

% Question 10: Support contact
\section*{Who can I contact for support?}
For technical support, reach out to our support team at huzaifamateen426@gmail.com.

\end{document}