\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\begin{document}

% Setting up the title
\title{Privacy Policy for SecureGen AI}
\author{}
\date{\today}
\maketitle

% Introduction to privacy commitment
\section*{Introduction}
At CodeMaestro, we are committed to protecting your privacy. This Privacy Policy explains how we collect, use, and safeguard your information when you use SecureGen AI, a network intrusion detection system (the ``Service'').

% Types of information collected
\section*{Information We Collect}
We collect the following types of information:
\begin{itemize}
    \item \textbf{Personal Information:} Name, email address, and other contact details provided during account registration.
    \item \textbf{Usage Data:} Information about your interactions with the Service, such as log data and web interface usage.
    \item \textbf{Federated Learning Data:} Encrypted model parameters from local training, but not your raw network data.
\end{itemize}

% Methods of data collection
\section*{How We Collect Information}
\begin{itemize}
    \item \textbf{Directly from You:} Through account creation and user inputs.
    \item \textbf{Automatically:} Via cookies and similar technologies to track usage.
    \item \textbf{Federated Learning:} Encrypted model parameters are sent from your local device to our servers for aggregation.
\end{itemize}

% Purposes of data usage
\section*{How We Use Information}
We use your information to:
\begin{itemize}
    \item Provide, maintain, and improve the Service.
    \item Communicate with you, including sending updates and support messages.
    \item Train machine learning models through federated learning, using encrypted parameters.
    \item Ensure security and prevent fraud.
\end{itemize}

% Data sharing practices
\section*{How We Share Information}
We may share your information:
\begin{itemize}
    \item With service providers who assist in operating the Service (e.g., cloud hosting).
    \item In aggregated or anonymized form for research or statistical purposes.
    \item As required by law or to protect our rights.
\end{itemize}

% Security measures
\section*{Data Security}
We employ industry-standard security measures, including CKKS homomorphic encryption for model parameters and Halo2 zero-knowledge proofs for authenticity verification, to protect your information.

% User rights under data protection laws
\section*{User Rights}
You have the right to:
\begin{itemize}
    \item Access, correct, or delete your personal information.
    \item Opt-out of certain data collection practices.
    \item Contact us at huzaifamateen426@gmail.com for assistance, with responses provided within one month.
\end{itemize}

% Policy update process
\section*{Changes to This Policy}
We may update this Privacy Policy periodically. Changes will be posted on this page, and we will notify you of significant updates.

% Contact information
\section*{Contact Us}
For questions about this Privacy Policy, please contact us at huzaifamateen426@gmail.com.

\end{document}