\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\begin{document}

% Setting up the title
\title{Terms and Conditions for SecureGen AI}
\author{}
\date{\today}
\maketitle

% Introduction to the agreement
\section*{Acceptance of Terms}
By accessing or using SecureGen AI, a network intrusion detection system (the ``Service''), you agree to be bound by these Terms and Conditions (``Terms''). If you do not agree to these Terms, you may not use the Service. These Terms constitute a binding agreement between you (``Customer'' or ``You'') and CodeMaestro.

% Describing the service
\section*{Description of Service}
SecureGen AI is a web-based network intrusion detection system that combines signature-based detection using Suricata with anomaly-based detection powered by machine learning. It employs federated learning for collaborative model training, ensuring data privacy through CKKS homomorphic encryption and Halo2 zero-knowledge proofs. The Service is designed to detect and mitigate cyber threats while maintaining compliance with data protection regulations.

% User account requirements
\section*{User Accounts}
To use the Service, you must create an account. You are responsible for maintaining the confidentiality of your account credentials and for all activities conducted under your account. You agree to notify CodeMaestro immediately of any unauthorized use of your account.

% Rules for using the service
\section*{Use of Service}
You may use the Service only for lawful purposes and in accordance with these Terms. You agree not to:
\begin{itemize}
    \item Use the Service in any way that violates applicable laws or regulations.
    \item Attempt to interfere with, damage, or disrupt the Service or its infrastructure.
    \item Use the Service to develop competing products or services.
\end{itemize}

% Intellectual property ownership
\section*{Intellectual Property}
The Service, including its software, algorithms, user interface, and documentation, is owned by CodeMaestro and protected by international copyright, trademark, patent, trade secret, and other intellectual property laws. You are granted a non-exclusive, non-transferable, non-sublicensable license to use the Service for internal purposes during the subscription term.

% Disclaimers and liability limitations
\section*{Disclaimers and Limitations of Liability}
The Service is provided ``as is'' without warranties of any kind, express or implied. CodeMaestro does not guarantee that the Service will detect all cyber threats or operate without errors. To the fullest extent permitted by law, CodeMaestro shall not be liable for any indirect, incidental, special, consequential, or punitive damages, including loss of profits, data, or business opportunities, arising from the use of the Service. Liability is limited to the fees paid for the Service during the subscription term.

% Termination conditions
\section*{Termination}
CodeMaestro may suspend or terminate your access to the Service at any time, without prior notice, for conduct that violates these Terms, poses a security threat, or for non-payment of fees (with reasonable notice). Upon termination, you must cease using the Service and delete any installed components.

% Governing law
\section*{Governing Law}
These Terms shall be governed by and construed in accordance with the laws of Jurisdiction. Any disputes shall be resolved in the courts of Jurisdiction.

% Contact information
\section*{Contact Information}
For questions about these Terms, please contact us at huzaifamateen426@gmail.com.

\end{document}